A quick user guide to the\\ \scine-\qcm\ software suite for \mol

### 2021-07-30 dmrg/doc/qcmaquis_manual.tex

%\clearpage
\clearpage
\newpage
\section{Additional Considerations}

>>>>

%\clearpage
\clearpage
\newpage

\subsection{QCMaquis pre-Born--Oppenheimer module}\label{sec:preBO}

The pre-Born--Oppenheimer (pre-BO) module within QCMaquis provides a tool to perform
DMRG-CASCI calculations of \textit{multicomponent} systems consisting of multiple spin-$\frac12$
particle types.

QCMaquis follows the formatting of the integral file shown in
Listing~\ref{lst:prebodump}. The first line with only a single float,
contains a constant shift in energy, e.g., point-charge repulsion of classical
nuclei.
The following lines contain the terms in the Hamiltonian where pairs of numbers
$m-n$ describe a single second-quantization operator. The first number denotes
the particle type (starting with 0) and the second number the orbital index of
the given particle type (also starting with 0 for all types). 
We assume physics notation and normal-ordering, i.e., the following would be a
valid term
\begin{equation}
  \left(\int \phi_{1-1}(1)\phi_{0-1}(2)g(1,2)\phi_{1-0}(1)\phi_{0-1}(2)\right)
  a^\dagger_{1-1} a^\dagger_{0-1} a_{0-1} a_{1-0}\,.
\end{equation}
The second and third lines contain single-paricle type \textit{hopping} terms.
The fourth line stands for a single-particle type interaction, and the fifth
line for an interaction between different particle types. 
Note here that the aforementioned convention implies that operators belonging to
the same particle types in a given string of operators must be either at
positions 1 and 4 or 2 and 3.

\begin{lstlisting}[language=qcmaquis,caption={Pre-BO integral file
format.},label=lst:prebodump]
1.145901278714102                       
   0-0         0-0                                      -2.451508889071943
   1-0         1-0                                      2.30233235666604
   0-2         0-0         0-1         0-1              -0.08690785254423253
   1-1         0-1         0-1         1-0              4.887021698358933e-05
\end{lstlisting}

Listing~\ref{lst:qcm} shows an input example for a pre-BO DMRG-FCI calculation. 
It assumes that a pre-BO integral file with has been generated. Additionally,
the 1-particle RDM and the mutual information can be measured and printed to a
file.

\begin{lstlisting}[language=qcmaquis,caption={Input example for a pre-BO DMRG-FCI
calculation},label=lst:preboinput]
nsweeps                         = 6
max_bond_dimension              = 1000

// Pre-BO specific input
// String with the number of parciles for each type
PreBO_ParticleTypeVector        = "4 1"
// Spin-1/2 fermion (1) or spin-0 boson (0)
// Attention: the boson-related functionality has not been fully tested, yet.
PreBO_FermionOrBosonVector      = "1 1"
// Number of orbitals for each type.
PreBO_OrbitalVector             = "3 3"
// Number of alpha-beta particles for each type
// Note: for spin-0 bosons it would be a single number.
PreBO_InitialStateVector        = "2 2 1 0"

optimization                    = twosite 
symmetry                        = nu1

model_library                   = coded
lattice_library                 = coded
LATTICE                         = "preBO lattice"

// Your model
MODEL                           = PreBO
init_state                      = 'default'

// Hamiltonian file
integral_file                   = FCIDUMP.E_4_H1_1
integral_cutoff                 = 1.0E-10

MEASURE[1rdm]          = 1
MEASURE[mutinf]        = 1
\end{lstlisting}

%\clearpage
\clearpage
\newpage

\section{Additional Considerations}
